\begin{acknowledgements}

I'm so unbelievably privileged to have such a large concentration of amazing people in my life. A proper acknowledgement is due, but this single page will have to suffice for now.

First I'd like to thank my advisor, Peter Samuelson. He has shown me nothing but good will and constant support, even during a global pandemic. He introduced me to some of the most beautiful mathematics I've ever seen. I will miss receiving from him brilliantly graceful answers to questions which seem so complicated. 

Thank you to Jackie for traveling across the country to join me in this wild adventure. Nothing would have been the same without you here with me. To my parents, Don and Denise, thank you for raising me to be who I am today. They've lifted me up at every step of the way and never doubted me. Thank you to my brothers, Tyler and Joey, and all of my friends (yes, all of you!) for helping me stay sane and keep on going. Thank you to Alberto Delgado and Tyler Robinson for really convincing me that I wasn't just some punk and that this really was possible. 

My professors have also been a huge inspiration to me along the way. It was an amazing experience being able to learn from such smart people. The grad students, especially my cohort, at UCR have also been inspiring people to work with. This past year has shown me how much I really took for granted being able to pop in to their offices anytime to talk about math (or often unrelated topics). A special thanks to the math department staff for keeping everything running behind the scenes for us.

Thanks to David Jordan, Peter Samuelson, Dan Freed, Olivier Schiffman, and all ICMS staff for organizing the 2019 GRT workshop at the ICMS in Edinburgh. My first major breakthrough, Theorem \ref{thm:powersumcommutator}, was proven there in my dorm at 4 a.m. while being unable to sleep due to jet lag and from the pure excitement of simply being there. This was the first time I truly felt like a mathematician, which influenced everything that followed.
\end{acknowledgements}
